SDSS-IV MaNGA: Mass-Independent Star Formation Enhancement in Close Galaxy Pairs

### 2020-08-18 maintex.tex
more edits
updated values

\title{
SDSS-IV MaNGA: Mass Independent Star Formation Enhancement in Close Galaxy Pairs
}

@@

\begin{abstract}
We study the spatial profile of the star formation rate (SFR) in a sample of {\it 220} interacting galaxies within the SDSS-IV MaNGA survey. We find that the specific star formation rate (sSFR) is centrally (e.g. within a single effective radius) enhanced in interacting galaxies by $\sim$0.25 $\pm$ 0.1 but that there is no enhancement or suppression in their disks. We split the radial profile into five separate stellar mass bins from \logm\ $=$ 9.0$-$11.5 and find that the sSFR enhancement has no dependence on the stellar mass of the paired galaxies. Within one effective radius, the sSFR enhancement in each of the mass bins falls within $\sim$0.1 dex of the median profile for the whole pair sample. We then use a second method to compare paired galaxies and control galaxies where each paired galaxies is matched to a set of 20 control galaxies based on stellar mass and redshift. The sSFR enhancements found are still mass independent, reinforcing the idea that low mass galaxies experience the same level of enhancement to their star formation rate as high mass galaxies. Since the merger induced sSFR enhancement is constant over stellar mass, low mass galaxies will experience a higher fractional mass growth rate of 1$-$7\%, assuming a constant burst merger induced star formation over a 1 Gyr period. This indicates that merger induced star formation has a significant impact on the mass evolution of low mass galaxies.

@@

Where NUV$-$r is the color and M$_i$ is the i-band magnitude from the NSA catalog.

On top of the color selection cuts, we require that all galaxies are in the Primary or Secondary MaNGA subsamples \citep{Wake:2017}. The resulting sample cover a stellar mass range of \logm\ $=$ 9.0$-$11.5.

@@

We use the BPT diagnostic \citep{Baldwin:1981} to remove spaxels which were not ionized by star formation. To separate ionization sources, we use the theoretical maximum starburst line from \citet{Kewley:2001} (Equation \ref{eq:kewley}).

\begin{equation}\label{eq:kewley}
\rm{log\Big(\frac{[O\,\textsc{iii}]\lambda 5007}{H\beta}\Big) = \frac{0.61}{log([N\,\textsc{ii}]\lambda 6584 / H\alpha) - 0.47} + 1.19}
\end{equation}

Where \OIII$\lambda$5007, H$\beta$, \NII$\lambda$6584, and H$\alpha$ are emission line fluxes within each MaNGA spaxel. We use the \citet{Kewley:2001} demarcation line as the limit for classifying star formation in the MaNGA spaxels.

It has also been shown that hot low mass evolved stars (HOLMES) in retired galaxies can mimic H\,{\sc ii} regions and AGN on the BPT diagram \citep{Stasinska:2008}. We apply an H$\alpha$ equivalent width (EW) cut of \ewha\ $>$ 3\AA\ to mask retired spaxels \citep{Cid-Fernandes:2011}.

@@

In order to spatially characterize the star formation in the paired galaxies we build radial profiles of sSFR. First, the geometry of the galaxies need to be defined.  We use the $r$-band elliptical Petrosian apertures from the NSA catalog and the $r$-band S\'ersic apertures from \citet{Simard:2011} to define the geometries of the galaxies.

@@

Once the stacked profile of the control galaxies is made, we take the difference between the paired galaxy's profile and the stacked control profile in log space. We do this process for each of the 160 paired galaxies.

@@

The difference profiles are shown to be centrally enhanced by $\sim$0.30 $\pm$ 0.1 dex. The enhancement falls to zero around 1.0 \reff\ and is slightly suppressed in their disks by $\sim$0.1 dex. The profiles of the pair stellar masses of \logm\ $=$ 9.0$-$9.5 show a strong enhancement in their disks of $\sim$0.1$-$0.2 $\pm$ 0.1 dex.

@@

We can also inspect the star formation enhancement within individual paired galaxies. We extract the $\Delta$log(sSFR) from the individual difference profiles. We extract the value of $\Delta$log(sSFR) from the inner 0.5 R/\reff\ of the paired galaxies and take the mean value of the $\Delta$log(sSFR) within the aperture. We depict the central $\Delta$log(sSFR) as a function of stellar mass in the right hand panel of Figure \ref{fig:ssfr_mass}. The mass independence can be clearly seen here as the paired galaxies within each stellar mass bin fall within 0.1 dex of the 0.3 dex $\Delta$log(sSFR) median.

@@

For this estimation we use a timescale of 1 Gyr, which is the order of the typical timescale between the passage of the first and second pericenters in dark-matter simulations \citep{Boylan-Kolchin:2008}.

@@

The fractional mass change is greatest in the less massive galaxies, $\Delta$M$_{merger}$/M$_{total}$ $=$ 0.065, while it is less substantial is the more massive galaxies, $\Delta$M$_{merger}$/M$_{total}$ $=$ 0.015. This is unsurprising as the $\Delta$log(sSFR) profiles were independent of the galaxies' total stellar mass.

Galaxies in the mass range \logm\ $=$ 9.0$-$10.0 have a mass growth of $\sim$1.6$\times$ that of secular mass growth and galaxies in the mass range \logm\ $=$ 10.0$-$11.0 have a mass growth of $\sim$2.3$\times$ that of secular mass growth. While low mass galaxies may see a more substantial change to their total stellar mass, the more massive galaxies experience higher growth rates.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=\linewidth]{fig/ssfr_partial.pdf}
\caption[]{Same as Figure \ref{fig:ssfr_mass} except the difference profiles are split by mass ratio (\textbf{Top row}) and projected separation (\textbf{Bottom row}). }
\label{fig:ssfr_dmsep}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

For the outside-IFU sample we use the stellar masses calculated from the r-band elliptical Petrosian apertures from the NSA catalog. For the inside-IFU sample, neither the NSA catalog nor \citet{Mendel:2014} will cover both galaxies. Instead we use stellar masses calculated from {\sc SPFIT} from the inner 2\arcsec\ of the galaxies.

In the Top row of Figure \ref{fig:ssfr_dmsep} we see that the sSFR enhancement is strongest in galaxies close to a 1:1 mass ratio, $\Delta$log(M) $=$ 0.0. These galaxies feature a central enhancement of $\sim$0.4 dex which is 0.15 dex higher than the average central enhancement of the whole sample. This enhancement falls with wider mass ratio; however, pairs with large differences in stellar mass still feature substantial levels of star formation enhancement, 0.2$-$0.25 dex at mass ratios of $|\Delta$log(M)$|$ $=$ 1.0.

@@

In previous studies it was noted that the enhancement to the SFR is strongest in galaxy pairs with small mass ratios \citet{Ellison:2008}. We see the same effect; however, we have also shown that galaxy pairs with large mass ratios still show a substantial level of sSFR enhancement. It has been a convention to split galaxy pairs in major mergers, $|$log(M)$|$ $\le$ 0.5, and minor mergers 0.5 $<$ $|$log(M)$|$ $\le$ 1.0. In this work, we can see that the mass ratio range used in galaxy pair studies could be widened to at least $|$log(M)$|$ $\le$ 2.0 so that larger pair samples can be constructed.

@@

We also look at the level of sSFR enhancement as a function of the projected separation between the two galaxies in the bottom row of Figure \ref{fig:ssfr_dmsep}. The $\Delta$log(sSFR) profiles show a clear gradient with the projected separation where close galaxy pairs show higher levels of sSFR enhancement compared to pairs with wide separations. The profiles in the galaxy pairs in the separation range, r$_p$ $=$ 0.0$-$12.5, are $\sim$0.1 dex above the median and the the profiles of the galaxy pairs in the separation range, r$_p$ $=$ 37.5$-$50.0, are $\sim$0.1 dex below the median.

This effect can be seen most clearly in the scatter plot of the central $\Delta$log(sSFR) enhancement as a function of projected separation. The level of the enhancement gradually increases with closer separation from 50 kpc to 10 kpc. While $\Delta$log(sSFR) falls at higher separations, there is still a substantial level of enhancement between 40 and 50 kpc, $\sim$0.1$-$0.2 dex. Within 15 kpc, the $\Delta$log(sSFR) enhancement jumps to 0.5$-$0.6 dex.

@@

For the galaxies with the closest separations, r$_p$ $<$ 5 kpc, $\Delta$log(sSFR) drops to zero. This is strange as we would expect that the closest pairs would show the strongest enhancements to their star formation as they are currently or have just passed the first pericenter. This seems odd as one would think that these galaxies should show the strongest enhancements to the sSFR.

This lack of $\Delta$log(sSFR) could be due to a couple of reasons. First, it may be due to the limited sampling of this separation range, there are only 6 paired galaxies in this range. A second explanation could be that we are observing merging galaxies which are just going though their first pericenter, but have yet to have the burst of star formation. Not enough time has elapsed for the gas inflows from the disks of the galaxies to reach the centers of the galaxies. The hydrodynamical simulations of \citet{Scudder:2012} show this delay in the burst of star formation, where the burst of star formation only reaches its peak after 0.3 Gyr after the passage of the first pericenter.

@@

The $\Delta$log(SFR) as a function of projected separation has been studied before with the SDSS survey \citep{Ellison:2008, Patton:2013, Scudder:2012, Bustamante:2020}. We compare the mentioned surveys with our own work in Figure \ref{fig:nuc_sep}. We find that our pairs generally feature higher level of SFR enhancement in their centers, by $\sim$0.0$-$0.2 dex. Further, we probe galaxies with projected separations below 5 kpc, a projected separation range not covered in previous works. As mentioned in Section \ref{sec:sep}, we find a $\Delta$log(SFR) of zero implying that we are viewing galaxies that are about to or have just passed their first pericenter.

@@

In Figure \ref{fig:prof_comp} we look at the $\Delta$log(sSFR) profile as a function of galactocentric radius between our work and previous works. \citet{Pan:2019} examines a set of paired galaxies in the MaNGA survey while \citet{Thorp:2019} examines a set of post-merger galaxies in the MaNGA survey. The galaxy pairs in \citet{Pan:2019} have sSFR enhancements that are roughtly $\sim$0.05$-$0.2 dex higher than our sample. The $\Delta$log(sSFR) profile is closest to our work at the centers of the galaxy pairs but then begins to diverge further out into the galaxies' disks. Our paired galaxies show zero sSFR enhancement in their disks past 1.0 R/\reff\ while the galaxy pairs in \citet{Pan:2019} show an enhancement of $\sim$0.15 dex to the sSFR in their disks.

The post-merger galaxies in \citet{Thorp:2019} have sSFR enhancements between $\sim$0.05$-$0.15 higher than our sample of paired galaxies. Their $\Delta$log(sSFR) profile follows our sample's profile closely between 0.25$-$1.0 R/\reff. The centers of the post-merger galaxies feature a greater level of sSFR enhancement in their centers compared to our galaxies pairs of $\Delta$log(sSFR) $=$ 0.5, roughly 0.25 dex higher than our paired galaxies. The post-merger galaxies also feature enhanced sSFR in their disk past 1.0 R/\reff\ of $\sim$0.1$-$0.15 dex. The heightened level of sSFR enhancement in the centers of post-merger galaxies in comparison to merging galaxies seems consistent with the idea that a second and greater burst of star formation occurs as the two merging galaxies coalesce into a single galaxy.

@@

In this work, we studied a sample of paired, star forming galaxies using the MaNGA IFS survey. We have made a sample of 160 star forming galaxy pairs along with a set of 1891 star forming control galaxies. We compared the radial profiles of the paired galaxies with those of the controls galaxies and found the follwing;

\begin{enumerate}
\item The sSFR is centrally enhanced within the inner 1.0 R/\reff\ by 0.30 $\pm$ 0.1 dex. 
\item The disks of the paired galaxies, R/\reff\ $=$ 1.0$-$2.5, show no signs of either sSFR enhancement or sSFR suppression. 
\item The sSFR enhancement in paired galaxies is independent of the total stellar mass of the paired galaxies, Massive galaxies experience the same level of sSFR enhancement as low mass galaxies.
\item The sSFR enhancement in paired galaxies does depend on the ratio between the masses of the paired galaxies. Galaxies with small mass ratios, $|\Delta$log(M)$|$ $=$ 0.0$-$0.5, see an enhancement to sSFR of 0.4 $\pm$ 0.1 dex, which is 0.15 dex higher than the average paired galaxies in the survey. We have also showed that paired galaxies with large mass ratios, 1.0 $<$ $|\Delta$log(M)$|$ $<$ 2.0, still show substantial levels of enhancement to the sSFR, 0.1$-$0.2 dex. 
\item Further, in paired galaxies with large mass ratios, the less massive galaxies experience higher levels of sSFR enhancement than the more massive galaxy in the pair, $\sim$0.1 dex.
\item The sSFR enhancement increases with closer projected separations where galaxies within 5$-$15 kpc have their sSFR enhanced by 0.5$-$0.6 $\pm$ 0.1 dex. The galaxies within 5 kpc experience no central enhancement to their sSFR. We believe that these galaxies have just passed their first pericenter and the merger induced gas-inflow have yet to reach the centers of these galaxies.
\item The paired galaxies will experience a faster mass growth rate of secular evolution of 1.6$-$2.3$\times$. The growth rate is highest for massive galaxies; however, the the low mass galaxies will see a higher fractional mass increase in comparison to the preexisting stellar mass.

>>>>

\title{
SDSS-IV MaNGA: Mass-Independent Star Formation Enhancement in Close Galaxy Pairs
}

@@

\begin{abstract}
We study the spatial profile of the star formation rate (SFR) in a sample of 220 interacting galaxies within the SDSS-IV MaNGA survey. We find that the specific star formation rate (sSFR) is centrally (e.g. within a single effective radius) enhanced in interacting galaxies by $\sim$0.25 $\pm$ 0.1 but that there is no enhancement or suppression in their disks. We split the radial profile into five separate stellar mass bins from \logm\ $=$ 9.0$-$11.5 and find that the sSFR enhancement has no dependence on the stellar mass of the paired galaxies. Within one effective radius, the sSFR enhancement in each of the mass bins falls within $\sim$0.1 dex of the median profile for the whole pair sample. We then use a second method to compare paired galaxies and control galaxies where each paired galaxies is matched to a set of 20 control galaxies based on stellar mass and redshift. The sSFR enhancements found are still mass independent, reinforcing the idea that low mass galaxies experience the same level of enhancement to their star formation rate as high mass galaxies. Since the merger induced sSFR enhancement is constant over stellar mass, low mass galaxies will experience a higher fractional mass growth rate of 1$-$6\%, assuming a constant burst merger induced star formation over a 1 Gyr period. This indicates that merger induced star formation has a significant impact on the mass evolution of low mass galaxies.

@@

Where NUV$-$r is the color and M$_i$ is the i-band magnitude from the NSA catalog. We have checked the selected star forming galaxies on the BPT diagram \citep{Baldwin:1981} and confirmed that there is not a significant number of AGN in our sample.

On top of the color selection cuts, we require that all galaxies are in the Primary or Secondary MaNGA subsamples \citep{Wake:2017}. The stellar mass range of the galaxy sample is between \logm\ $=$ 9.0$-$11.5.

@@

%We use the BPT diagnostic \citep{Baldwin:1981} to remove spaxels which were not ionized by star formation. To separate ionization sources, we use the theoretical maximum starburst line from \citet{Kewley:2001} (Equation \ref{eq:kewley}).

%\begin{equation}\label{eq:kewley}
%\rm{log\Big(\frac{[O\,\textsc{iii}]\lambda 5007}{H\beta}\Big) = \frac{0.61}{log([N\,\textsc{ii}]\lambda 6584 / H\alpha) - 0.47} + 1.19}
%\end{equation}

%Where \OIII$\lambda$5007, H$\beta$, \NII$\lambda$6584, and H$\alpha$ are emission line fluxes within each MaNGA spaxel. We use the \citet{Kewley:2001} demarcation line as the limit for classifying star formation in the MaNGA spaxels.

It has been shown that hot low mass evolved stars (HOLMES) in retired galaxies can mimic H\,{\sc ii} regions and AGN on the BPT diagram \citep{Stasinska:2008}. To mask retired spaxels, we implement a H$\alpha$ equivalent width (EW) cut of \ewha\ $>$ 3\AA\ \citep{Cid-Fernandes:2011}.

@@

In order to spatially characterize the star formation in the paired galaxies we build radial profiles of sSFR. First, the geometry of the galaxies need to be defined. Specifically we will need position angle, inclination angle, and the effective radius of each of the MaNGA targets. We use the $r$-band elliptical Petrosian apertures from the NSA catalog and the $r$-band S\'ersic apertures from \citet{Simard:2011} to define the geometries of the galaxies.

@@

Once the stacked profile of the control galaxies is made, we take the difference between the paired galaxy's profile and the stacked control profile in log space. We do this process for each of the 220 paired galaxies.

@@

The difference profiles are shown to be centrally enhanced by $\sim$0.25 $\pm$ 0.1 dex. The enhancement falls to zero around 1.0 \reff\ and is slightly suppressed in their disks by $\sim$0.1 dex. The profiles of the pair stellar masses of \logm\ $=$ 9.0$-$9.5 show a strong enhancement in their disks of $\sim$0.1$-$0.2 $\pm$ 0.1 dex.

@@

We can also inspect the star formation enhancement within individual paired galaxies. We extract the $\Delta$log(sSFR) from the individual difference profiles. We extract the value of $\Delta$log(sSFR) from the inner 0.5 R/\reff\ of the paired galaxies and take the mean value of the $\Delta$log(sSFR) within the aperture. We depict the central $\Delta$log(sSFR) as a function of stellar mass in the right hand panel of Figure \ref{fig:ssfr_mass}. The mass independence can be clearly seen here as the paired galaxies within each stellar mass bin fall within 0.1 dex of the 0.2 dex $\Delta$log(sSFR) median.

@@

For this estimation we use a timescale of 1 Gyr, which is the order of the typical timescale between the passage of the first and second pericenters in dark-matter simulations \citep{Boylan-Kolchin:2008}. The actual timescale for star formation enhancement is likely shorter; however, we use the 1 Gyr value as an order of magnitude guess.

@@

The fractional mass change is greatest in the less massive galaxies, $\Delta$M$_{merger}$/M$_{total}$ $=$ 0.06 (6\%), while it is less substantial is the more massive galaxies, $\Delta$M$_{merger}$/M$_{total}$ $=$ 0.005 (0.5\%). This is unsurprising as the $\Delta$log(sSFR) profiles were independent of the galaxies' total stellar mass.

%Galaxies in the mass range \logm\ $=$ 9.0$-$10.0 have a mass growth of $\sim$1.6$\times$ that of secular mass growth and galaxies in the mass range \logm\ $=$ 10.0$-$11.0 have a mass growth of $\sim$2.3$\times$ that of secular mass growth. While low mass galaxies may see a more substantial change to their total stellar mass, the more massive galaxies experience higher growth rates.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=\linewidth]{fig/ssfr_partial.pdf}
\caption[]{{\it Use larger bins here.} Same as Figure \ref{fig:ssfr_mass} except the difference profiles are split by mass ratio (\textbf{Top row}) and projected separation (\textbf{Bottom row}). }
\label{fig:ssfr_dmsep}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

For the outside-IFU sample we use the stellar masses calculated from the r-band elliptical Petrosian apertures from the NSA catalog. Most of the companion galaxies in the inside-IFU sample are not covered by either the NSA catalog or \citet{Simard:2011}. Because of this, the inside-IFU galaxies are left out of this analysis.

In the Top row of Figure \ref{fig:ssfr_dmsep} we see that the sSFR enhancement is strongest in galaxies close to a 1:1 mass ratio, $\Delta$log(M) $=$ 0.0. These galaxies feature a central enhancement of $\sim$0.3 dex which is 0.1 dex higher than the average central enhancement of the whole sample. This enhancement falls with wider mass ratio; however, pairs with large differences in stellar mass still feature substantial levels of star formation enhancement, 0.15$-$0.20 dex at mass ratios of $|\Delta$log(M)$|$ $=$ 1.0.

@@

In previous studies it was noted that the enhancement to the SFR is strongest in galaxy pairs with small mass ratios \citet{Ellison:2008}. We see the same effect; however, we have also shown that galaxy pairs with large mass ratios still show a substantial level of sSFR enhancement. It has been a convention to split galaxy pairs in major mergers, $|$log(M)$|$ $\le$ 0.5, and minor mergers 0.5 $<$ $|$log(M)$|$ $\le$ 1.0. In this work, we can see that the mass ratio range used in galaxy pair studies could be widened to at least $|$log(M)$|$ $\le$ 1.5 so that larger pair samples can be constructed.

@@

We also look at the level of sSFR enhancement as a function of the projected separation between the two galaxies in the bottom row of Figure \ref{fig:ssfr_dmsep}. The $\Delta$log(sSFR) profiles show a clear gradient with the projected separation where close galaxy pairs show higher levels of sSFR enhancement compared to pairs with wide separations. The profiles in the galaxy pairs in the separation range, r$_p$ $=$ 0.0$-$12.5, are generally $\sim$0.1 dex above the median and the the profiles of the galaxy pairs in the separation range, r$_p$ $=$ 37.5$-$50.0, are generally $\sim$0.1 dex below the median.

This effect can be seen most clearly in the scatter plot of the central $\Delta$log(sSFR) enhancement as a function of projected separation. The level of the enhancement gradually increases with closer separation from 50 kpc to 10 kpc. While $\Delta$log(sSFR) falls at higher separations, there is still a substantial level of enhancement between 40 and 50 kpc, $\sim$0.1$-$0.2 dex. Within 15 kpc, the $\Delta$log(sSFR) enhancement jumps to 0.3$-$0.4 dex.

@@

For galaxies with separations of r$_p$ $<$ 5 kpc and r$_p$ $=$ 30$-$35 kpc we find a $\Delta$log(sSFR) of zero. For the r$_p$ $<$ 5 kpc galaxy, about half of the pairs show signs of tidal features while the others do not. The pairs without the tidal features may be approaching their first pericenter, meaning that the merger-induced gas-inflows have not been triggered yet. The dips in $\Delta$log(sSFR) may also just be due to statistical error from the relatively limited sample size.

@@

The $\Delta$log(SFR) as a function of projected separation has been studied before with the SDSS survey \citep{Ellison:2008, Patton:2013, Scudder:2012, Bustamante:2020}. We compare the mentioned surveys with our own work in Figure \ref{fig:nuc_sep}. We find that our central SFR enhancements are higher than many of the previous studies, the enhancements are $\sim$0.15 dex higher than \citet{Scudder:2012} and $\sim$0.25 dex higher than \citet{Ellison:2008} and \citet{Bustamante:2020}. Our $\Delta$log(SFR) as a function of projected separation is very consistent to what was found in \citet{Patton:2013}.

@@

In Figure \ref{fig:prof_comp} we look at the $\Delta$log(sSFR) profile as a function of galactocentric radius between our work and previous works. \citet{Pan:2019} examines a set of paired galaxies in the MaNGA survey while \citet{Thorp:2019} examines a set of post-merger galaxies in the MaNGA survey. The galaxy pairs in \citet{Pan:2019} have sSFR enhancements that are roughtly $\sim$0.1$-$0.2 dex higher than our sample. The $\Delta$log(sSFR) profile is closest to our work at the centers of the galaxy pairs but then begins to diverge further out into the galaxies' disks. Our paired galaxies show a slight sSFR suppression in their disks past 1.0 R/\reff\ while the galaxy pairs in \citet{Pan:2019} show an enhancement of $\sim$0.15 dex to the sSFR in their disks.

The post-merger galaxies in \citet{Thorp:2019} have sSFR enhancements between $\sim$0.05$-$0.2 higher than our sample of paired galaxies. The centers of the post-merger galaxies feature a greater level of sSFR enhancement in their centers compared to our galaxies pairs of $\Delta$log(sSFR) $=$ 0.5, roughly 0.25 dex higher than our paired galaxies. The post-merger galaxies also feature enhanced sSFR in their disk past 1.0 R/\reff\ of $\sim$0.1$-$0.15 dex. The heightened level of sSFR enhancement in the centers of post-merger galaxies in comparison to merging galaxies seems consistent with the idea that a second and greater burst of star formation occurs as the two merging galaxies coalesce into a single galaxy.

@@

In this work, we studied a sample of paired, star forming galaxies using the MaNGA IFS survey. We have made a sample of 220 star forming galaxy pairs along with a set of 1891 star forming control galaxies. We compared the radial profiles of the paired galaxies with those of the controls galaxies and found the follwing;

\begin{enumerate}
\item The sSFR is centrally enhanced within the inner 1.0 R/\reff\ by 0.25 $\pm$ 0.1 dex. 
\item The disks of the paired galaxies, R/\reff\ $=$ 1.0$-$2.5, show limited suppression in their disks, $\sim$0.1 dex.
\item The sSFR enhancement in paired galaxies is independent of the total stellar mass of the paired galaxies, Massive galaxies experience the same level of sSFR enhancement as low mass galaxies.
\item The sSFR enhancement in paired galaxies does depend on the ratio between the masses of the paired galaxies. Galaxies with small mass ratios, $|\Delta$log(M)$|$ $=$ 0.0$-$0.5, see an enhancement to sSFR of 0.3 $\pm$ 0.1 dex, which is 0.1 dex higher than the average paired galaxies in the survey. We have also showed that paired galaxies with large mass ratios, $|\Delta$log(M)$|$ $=$ 1.0, still show substantial levels of enhancement to the sSFR, 0.15$-$0.2 dex. 
\item Further, in paired galaxies with large mass ratios, the less massive galaxies experience higher levels of sSFR enhancement than the more massive galaxy in the pair, $\sim$0.1 dex.
\item The sSFR enhancement increases with closer projected separations where galaxies within 5$-$15 kpc have their sSFR enhanced by 0.3$-$0.4 $\pm$ 0.1 dex. 
\item The paired galaxies will experience a fractional mass growth rate of 1$-$6\%, where the growth in mass in largest in low mass galaxies.
